---
title: "YHPA.locator"
format:
  html:
    code-fold: show
    code-tools: true
toc: true
toc-title: Document Contents
number-sections: true
embed-resources: true
---

## Running Locator on YHPA Samples

## Testing locator - trying to predict locality of ao_MLZ_48333 (Tamaulipas)

#### Load libraries

```{r}
library(SNPfiltR)
library(vcfR)
library(ggplot2)
library(stringr)
library(StAMPP)
library(adegenet)
library(tidyverse)
library(sf)
library(rnaturalearth)
library(geosphere)
```

#### Read in vcf and popmap

```{r}
#| output: false
vcfR<-read.vcfR("~/Dropbox/08_yhpa_072025/yhpa_final_filtered_unlinked.vcf.gz")
vcfR

popmap<-read.csv("~/Dropbox/08_yhpa_072025/oratrix_popmap.csv")
popmap

#make sure sampling file matches vcf
popmap$id %in% colnames(vcfR@gt)[-1]
colnames(vcfR@gt)[-1] %in% popmap$id
```

#### Creating vcf for locator

Using filtered vcf with 80% threshold and thinned created using `oratrix_snp_filtering.qmd`. This vcf corresponds to the samples in the sample data document locator uses to predict localities `sample_data_tamaulipas_test.txt`.

```{r}
#removing 7 Belize samples with the most missing data (only keeping 2 samples with the most data for balance)
miss<-missing_by_sample(vcfR)

#we need to remove socal samples (ao_MLZ_1105, ao_MLZ_70063, and ao_MLZ_70074) since we do not know their origin
#removing confiscated scp samples because we don't have their localities
test.vcf<-(vcfR)[, !colnames((vcfR)@gt) %in% c("ao_MLZ_1105", #socal
                                               "ao_MLZ_70063", #socal
                                               "ao_MLZ_70074", #socal
                                               "ao_BC_108", #belize
                                               "ao_BC_109", #belize
                                               "ao_BC_A113", #belize
                                               "ao_BC_A114", #belize
                                               "ao_BC_A116", #belize
                                               "ao_BC_A117", #belize
                                               "ao_BC_A118", #belize
                                               "ao_SP_1", #all SP samples confiscated
                                               "ao_SP_2",
                                               "ao_SP_3",
                                               "ao_SP_4",
                                               "ao_SP_5",
                                               "ao_SP_6",
                                               "ao_SP_7",
                                               "ao_SP_8",
                                               "ao_SP_831",
                                               "ao_SP_832",
                                               "ao_SP_833",
                                               "ao_SP_834",
                                               "ao_SP_835",
                                               "ao_SP_836",
                                               "ao_SP_837",
                                               "ao_SP_838",
                                               "ao_SP_839",
                                               "ao_SP_840")]

test.vcf
```

#### Create popmap and save vcf

```{r}
#subset popmap to only include retained individuals
popmap<-popmap[popmap$id %in% colnames(test.vcf@gt),]

#make sure sampling file matches vcf
popmap$id %in% colnames(test.vcf@gt)[-1]
colnames(test.vcf@gt)[-1] %in% popmap$id

#reorder sampling file to match order of samples in vcf
sample.info<-popmap[match(colnames(test.vcf@gt)[-1], popmap$id),]
popmap$id == colnames(test.vcf@gt)[-1]

test.vcf.mac2<-min_mac(test.vcf, min.mac = 2)

# vcfR:: write.vcf(test.vcf.mac2, "~/Dropbox/08_yhpa_072025/locator/final_runs/tamaulipas_run/tamaulipas.mac2.unlinked.subsampled.belize.vcf.gz")

test.vcf.mac2

#confirm sample sheet matches the samples in the vcf
test_sample_data<-read_delim("~/Dropbox/08_yhpa_072025/locator/final_runs/tamaulipas_run/sample_data_tamaulipas_subsampled_belize.txt")

colnames(test.vcf.mac2@gt)
test_sample_data$sampleID

test_sample_data$sampleID %in% colnames(test.vcf.mac2@gt)[-1]
colnames(test.vcf.mac2@gt)[-1] %in% test_sample_data$sampleID
```

#### In command line `locator_tamaulipas_test.sh` using Occidental College's HPC Cluster Bletchley

```         
#!/bin/sh
#
#SBATCH --job-name=locator_tamaulipas             # Job Name
#SBATCH --partition=mlz-medium         # Name of the Slurm partition used
#SBATCH --nodelist=n028

locator --vcf /home/ramirezb/oratrix_locator/data/tamaulipas.mac2.unlinked.subsampled.belize.vcf.gz --sample_data /home/ramirezb/oratrix_locator/data/sample_data_tamaulipas_subsampled_belize.txt --out /home/ramirezb/oratrix_locator/out_tamaulipas_final/oratrix --bootstrap --nboots 200 --train_split 0.7 --nlayers 6 --seed 641
```

#### Testing to see if locator predicted the correct locality

```{r}
setwd("~/Dropbox/08_yhpa_072025/locator/")

#all data
all_data<-read_delim("~/Desktop/oratrix_locator/all_samples_sample_data.txt")

locator_test<-all_data[all_data$sampleID %in% c("ao_MLZ_48333"),]
locator_test$y<-as.numeric(locator_test$y)
```

#### Read in shapefiles

```{r}
#map
yhpa_map <- ne_countries(country = c("Guatemala", "Belize", "El Salvador",
                                     "Honduras", "Nicaragua", "Costa Rica", "Panama"), returnclass = "sf") 

mx_states<-ne_states("Mexico", returnclass = "sf")

#yhpa range
yhpa_shp<-st_read("~/Dropbox/08_yhpa_072025/iucn_shp_files/trimmed_shapefiles/trimmed_yhpa.shp")
```

#### Load in the predictions

```{r}
#| output: false
setwd("~/Dropbox/08_yhpa_072025/locator/final_runs/tamaulipas_run/out_tamaulipas_final")
# Get list of all predloc files
files <- list.files(pattern = "predlocs.*\\.txt")
files
#remove full run
files <- files[-c(201)]

#This is the prediction from the full model trained on all SNPs (no resampling)
full<-read_delim("oratrix_bootFULL_predlocs.txt")

# Read and bind them - all bootstrapped predictions
all_preds <- files %>%
  map_df(~ read_delim(.x, delim = ",", col_names = TRUE), .id = "file")

individual_means <- all_preds %>%
  group_by(sampleID) %>%
  summarize(mean_long = mean(y, na.rm = TRUE),
            mean_lat = mean(x, na.rm = TRUE))

summary_stats<-all_preds %>%
  group_by(sampleID) %>%
  summarize(mean_long = mean(y, na.rm = TRUE),
            mean_lat = mean(x, na.rm = TRUE),
            sd_x = sd(x, na.rm = TRUE),
            sd_y = sd(y, na.rm = TRUE))

#model performance
# R2(x)=0.9048874401793426
# R2(y)=0.7251666190870507
# mean validation error 4.500907480553764
# median validation error 2.096568170925232

#calculate distance the predictions are from the actual locality
df_mean <- locator_test %>%
  inner_join(individual_means, by = "sampleID") %>%
  mutate(
    dist_km_mean = distHaversine(
      cbind(y, x),                 # true location (lon, lat)
      cbind(mean_long, mean_lat)   # mean prediction (lon, lat)
    ) / 1000
  )

df_full <- locator_test %>%
  inner_join(full, by = "sampleID") %>%
  mutate(
    dist_km_full = distHaversine(
      cbind(locator_test$y, locator_test$x),     # true location
      cbind(full$y, full$x)  # full prediction (renamed cols after join)
    ) / 1000
  )

distance_df <- df_mean %>%
  select(sampleID, dist_km_mean) %>%
  left_join(df_full %>% select(sampleID, dist_km_full), by = "sampleID")

distance_df

distance_line_means <- data.frame(
  true_x = locator_test$x,
  true_y = locator_test$y,
  pred_x = individual_means$mean_lat,
  pred_y = individual_means$mean_long
)

distance_line_full <- data.frame(
  true_x = locator_test$x,
  true_y = locator_test$y,
  pred_x = full$x,
  pred_y = full$y
)
```

#### Plotting predictions

```{r}
#showing 200 predictions
# tamaulipas_test<-
  ggplot() +
  geom_sf(data = yhpa_map, fill = "gray95", color = "black") +
  geom_sf(data = mx_states, fill="gray95") +
  geom_sf(data = yhpa_shp, fill = "cornsilk2", show.legend = FALSE) +
  geom_point(data = all_preds, aes(x = y, y = x, col = "all 200 bootstrapped predictions for unknown sample"), alpha = 0.4, size=2) +
  geom_point(data = individual_means, aes(x = mean_long, y = mean_lat, color = "mean of 200 bootstraps"), size = 2) +
  geom_point(data = full, aes(x = y, y = x,  color = "prediction from all samples - all SNPs with no resampling"), size = 2) +
  geom_point(data = test_sample_data, aes(x = y, y = x, color = "all yhpa callibration points"), size = 2) +
  geom_point(data = locator_test, aes(x = y, y = x, col = "real location of ao_MLZ_48333"), size = 2) +
    
  #adding in distance between true locality and prediction  
   #mean prediction: 333.812	km
   geom_segment(data = distance_line_means,
               aes(x = true_y, y = true_x, xend = pred_y, yend = pred_x),
               color = "black", linetype = "dashed") +
   #full prediction: 384.2968	km
   geom_segment(data = distance_line_full,
               aes(x = true_y, y = true_x, xend = pred_y, yend = pred_x),
               color = "black", linetype = "dashed") +
    
    scale_color_manual(
    values = c(
      "all 200 bootstrapped predictions for unknown sample" = "palevioletred",
      "mean of 200 bootstraps" = "forestgreen",
      "prediction from all samples - all SNPs with no resampling" = "skyblue",
      "all yhpa callibration points" = "gray27",
      "real location of ao_MLZ_48333" = "#ffab00"
    )
  ) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = c(1, 0.6)) +
  labs(title = "Locator Predicted Origins (Tamaulipas test)",
  x = "Longitude", y = "Latitude")

#ggsave(tamaulipas_test,
#       filename="~/Dropbox/08_yhpa_072025/figures/locator/tamaulipas_test.svg",
#       device="svg",
#       dpi = 400, width = 12, height = 6)
```

```{r}
#showing 95% boostrap ellipse
# tamaulipas_ellipse<-
  ggplot() +
  geom_sf(data = yhpa_map, fill = "gray95", color = "black") +
  geom_sf(data = mx_states, fill="gray95") +
  geom_sf(data = yhpa_shp, fill = "cornsilk2", show.legend = FALSE) +
  # geom_point(data = all_preds, aes(x =y, y =x, col = "all 200 bootstrapped predictions for unknown sample"), alpha = 0.4) +
  # Ellipse around bootstrapped points
  stat_ellipse(data = all_preds, aes(x = y, y = x, color = "bootstrapped 95% ellipse"), level = 0.95, linetype = 2, linewidth = 1) +
  geom_point(data = individual_means, aes(x = mean_long, y = mean_lat, color = "mean of 200 bootstraps"), size = 2) +
  geom_point(data = full, aes(x = y, y = x,  color = "prediction from all samples - all SNPs with no resampling"), size = 2) +
  geom_point(data = test_sample_data, aes(x = y, y = x, color = "all yhpa callibration points"), size = 2) +
  geom_point(data = locator_test, aes(x = y, y = x, col = "real location of ao_MLZ_48333"), size = 2) +
    
  #adding in distance between true locality and prediction  
   #mean prediction: 333.812	km
   geom_segment(data = distance_line_means,
               aes(x = true_y, y = true_x, xend = pred_y, yend = pred_x),
               color = "black", linetype = "dashed") +
   #full prediction: 384.2968	km
   geom_segment(data = distance_line_full,
               aes(x = true_y, y = true_x, xend = pred_y, yend = pred_x),
               color = "black", linetype = "dashed") +
    
  scale_color_manual(
    values = c(
      "bootstrapped 95% ellipse" = "palevioletred",
      "mean of 200 bootstraps" = "forestgreen",
      "prediction from all samples - all SNPs with no resampling" = "skyblue",
      "all yhpa callibration points" = "gray30",
      "real location of ao_MLZ_48333" = "#ffab00"
    )
  ) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = c(1, 0.6)) +
  labs(title = "Locator Predicted Origins (Tamaulipas test)",
  x = "Longitude", y = "Latitude")
  
# ggsave(tamaulipas_ellipse,
#        filename="~/Dropbox/08_yhpa_072025/figures/locator/tamaulipas_test_ellipse.svg",
#        device="svg",
#        dpi = 400, width = 12, height = 6)
```

------------------------------------------------------------------------

## Predicting yhpa samples

```{r}
#we need to remove socal samples (ao_MLZ_1105, ao_MLZ_70063, and ao_MLZ_70074) since we do not know their origin
#need to downsample Belize again
#now trying to predict confiscated scp samples because we don't have their localities
yhpa.scp.vcf<-(vcfR)[, !colnames((vcfR)@gt) %in% c("ao_BC_108", #belize
                                                   "ao_BC_109", #belize
                                                   "ao_BC_A113", #belize
                                                   "ao_BC_A114", #belize
                                                   "ao_BC_A116", #belize
                                                   "ao_BC_A117", #belize
                                                   "ao_BC_A118", #belize
                                                   "ao_MLZ_1105", #socal
                                                   "ao_MLZ_70063", #socal
                                                   "ao_MLZ_70074")] #socal

yhpa.scp.vcf
```

```{r}
popmap<-read.csv("~/Dropbox/08_yhpa_072025/oratrix_popmap.csv")
popmap

#subset popmap to only include retained individuals
popmap<-popmap[popmap$id %in% colnames(yhpa.scp.vcf@gt),]

#make sure sampling file matches vcf
popmap$id %in% colnames(yhpa.scp.vcf@gt)[-1]
colnames(yhpa.scp.vcf@gt)[-1] %in% popmap$id

#reorder sampling file to match order of samples in vcf
sample.info<-popmap[match(colnames(yhpa.scp.vcf@gt)[-1], popmap$id),]
popmap$id == colnames(yhpa.scp.vcf@gt)[-1]

yhpa.scp.vcf.mac2<-min_mac(yhpa.scp.vcf, min.mac = 2)

# vcfR:: write.vcf(yhpa.scp.vcf.mac2, "~/Dropbox/08_yhpa_072025/locator/final_runs/yhpa_run/yhpa.mac2.unlinked.subsampled.vcf.gz")

yhpa.scp.vcf.mac2

#confirm sample sheet matches the samples in the vcf
yhpa_sample_data<-read.delim("~/Dropbox/08_yhpa_072025/locator/final_runs/yhpa_run/final_sample_data_yhpa.txt")

colnames(yhpa.scp.vcf.mac2@gt)
yhpa_sample_data$sampleID

yhpa_sample_data$sampleID %in% colnames(yhpa.scp.vcf.mac2@gt)[-1]
colnames(yhpa.scp.vcf.mac2@gt)[-1] %in% yhpa_sample_data$sampleID 
```

In Bletchley run `final_yhpa_locator.sh`

```         
#!/bin/sh
#
#SBATCH --job-name=locator_yhpa             # Job Name
#SBATCH --partition=mlz-medium         # Name of the Slurm partition used
#SBATCH --nodelist=n028

locator --vcf /home/ramirezb/oratrix_locator/data/yhpa.mac2.unlinked.subsampled.vcf.gz --sample_data /home/ramirezb/oratrix_locator/data/final_sample_data_yhpa.txt --out /home/ramirezb/oratrix_locator/out_yhpa_final/oratrix --bootstrap --nboots 200 --train_split 0.7 --nlayers 6 --seed 378
```

```{r}
#| output: false
setwd("~/Dropbox/08_yhpa_072025/locator/final_runs/yhpa_run/out_yhpa_final")
# Get list of all predloc files
yhpa_files <- list.files(pattern = "predlocs.*\\.txt")
yhpa_files
#remove full run
yhpa_files <- yhpa_files[-c(201)]

#This is the prediction from the full model trained on all SNPs (no resampling)
yhpa_full<-read_delim("oratrix_bootFULL_predlocs.txt")

# Read and bind them - all bootstrapped predictions
yhpa_all_preds <- yhpa_files %>%
  map_df(~ read_delim(.x, delim = ",", col_names = TRUE), .id = "file")

yhpa_individual_means <- yhpa_all_preds %>%
  group_by(sampleID) %>%
  summarize(mean_long = mean(x, na.rm = TRUE),
            mean_lat = mean(y, na.rm = TRUE))

yhpa_summary_stats<-yhpa_all_preds %>%
  group_by(sampleID) %>%
  summarize(mean_long = mean(x, na.rm = TRUE),
            mean_lat = mean(y, na.rm = TRUE),
            sd_x = sd(x, na.rm = TRUE),
            sd_y = sd(y, na.rm = TRUE))

#model performance
# R2(x)=0.9204751931039864
# R2(y)=0.7462154483480632
# mean validation error 3.088783654069266
# median validation error 2.6059843971358085
```

```{r}
#showing 200 predictions
# confiscated_yhpa<-
ggplot() +
  geom_sf(data = yhpa_map, fill = "gray95", color = "black") +
  geom_sf(data = mx_states, fill="gray95") +
  geom_sf(data = yhpa_shp, fill = "cornsilk2", show.legend = FALSE) +
  geom_point(data = yhpa_all_preds, aes(x =y, y =x, col = "all 200 bootstrapped predictions for unknown sample"), alpha = 0.4, size = 2) +
  geom_point(data = yhpa_individual_means, aes(x = mean_lat, y = mean_long, color = "mean of 200 bootstraps"), size = 2) +
  geom_point(data = yhpa_full, aes(x = y, y = x,  color = "prediction from all samples - all SNPs with no resampling"), size = 2) +
  geom_point(data = yhpa_sample_data, aes(x = y, y = x, color = "all yhpa callibration points"), size = 2) +
    scale_color_manual(
    values = c(
      "all 200 bootstrapped predictions for unknown sample" = "palevioletred",
      "mean of 200 bootstraps" = "forestgreen",
      "prediction from all samples - all SNPs with no resampling" = "skyblue",
      "all yhpa callibration points" = "gray27"
    )
  ) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = c(1, 0.6)) +
  labs(title = "Locator Confiscated YHPA Predictions",
  x = "Longitude", y = "Latitude")

# ggsave(confiscated_yhpa,
#        filename="~/Dropbox/08_yhpa_072025/figures/locator/confiscated_yhpa.svg",
#        device="svg",
#        dpi = 400, width = 12, height = 6)
```

```{r}
#showing 95% boostrap ellipse
# confiscated_ellipse<-
  ggplot() +
  geom_sf(data = yhpa_map, fill = "gray95", color = "black") +
  geom_sf(data = mx_states, fill="gray95") +
  geom_sf(data = yhpa_shp, fill = "cornsilk2", show.legend = FALSE) +
  # geom_point(data = yhpa_all_preds, aes(x =y, y =x, col = "all 200 bootstrapped predictions for unknown sample"), alpha = 0.4) +
  # Ellipse around bootstrapped points
  stat_ellipse(data = yhpa_all_preds, aes(x = y, y = x, group = sampleID, color = "bootstrapped 95% ellipse"),
    level = 0.95, linewidth = 0.4, linetype = 2, alpha = 0.5, 
    inherit.aes = FALSE, show.legend = FALSE) +
  geom_point(data = yhpa_individual_means, aes(x = mean_lat, y = mean_long, color = "mean of 200 bootstraps"), size = 2) +
  geom_point(data = yhpa_full, aes(x = y, y = x,  color = "prediction from all samples - all SNPs with no resampling"), size = 2) +
  geom_point(data = yhpa_sample_data, aes(x = y, y = x, color = "all yhpa callibration points"), size = 2) +
    scale_color_manual(
    values = c(
      "bootstrapped 95% ellipse" = "palevioletred",
      "mean of 200 bootstraps" = "forestgreen",
      "prediction from all samples - all SNPs with no resampling" = "skyblue",
      "all yhpa callibration points" = "gray27"
    )
  ) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = c(1, 0.6)) +
  labs(title = "Locator Confiscated YHPA Predictions",
  x = "Longitude", y = "Latitude")

# ggsave(confiscated_ellipse,
#        filename="~/Dropbox/08_yhpa_072025/figures/locator/confiscated_yhpa_ellipse.svg",
#        device="svg",
#        dpi = 400, width = 12, height = 6)
```

------------------------------------------------------------------------

## Predicting Southern California samples

```{r}
#we want to find localities of southern california samples (ao_MLZ_1105, ao_MLZ_70063, and ao_MLZ_70074)
#need to downsample Belize again
#removing confiscated scp samples because we don't have their localities
socal.vcf<-(vcfR)[, !colnames((vcfR)@gt) %in% c("ao_BC_108", #belize
                                                "ao_BC_109", #belize
                                                "ao_BC_A113", #belize
                                                "ao_BC_A114", #belize
                                                "ao_BC_A116", #belize
                                                "ao_BC_A117", #belize
                                                "ao_BC_A118", #belize
                                                "ao_SP_1", #all SP samples confiscated
                                                "ao_SP_2",
                                                "ao_SP_3",
                                                "ao_SP_4",
                                                "ao_SP_5",
                                                "ao_SP_6",
                                                "ao_SP_7",
                                                "ao_SP_8",
                                                "ao_SP_831",
                                                "ao_SP_832",
                                                "ao_SP_833",
                                                "ao_SP_834",
                                                "ao_SP_835",
                                                "ao_SP_836",
                                                "ao_SP_837",
                                                "ao_SP_838",
                                                "ao_SP_839",
                                                "ao_SP_840")]

socal.vcf
```

```{r}
popmap<-read.csv("~/Dropbox/08_yhpa_072025/oratrix_popmap.csv")
popmap

#subset popmap to only include retained individuals
popmap<-popmap[popmap$id %in% colnames(socal.vcf@gt),]

#make sure sampling file matches vcf
popmap$id %in% colnames(socal.vcf@gt)[-1]
colnames(socal.vcf@gt)[-1] %in% popmap$id

#reorder sampling file to match order of samples in vcf
sample.info<-popmap[match(colnames(socal.vcf@gt)[-1], popmap$id),]
popmap$id == colnames(socal.vcf@gt)[-1]

socal.vcf.mac2<-min_mac(socal.vcf, min.mac = 2)

# vcfR:: write.vcf(socal.vcf, "~/Dropbox/08_yhpa_072025/locator/final_runs/socal_run/socal.mac2.unlinked.subsampled.vcf.gz")

socal.vcf.mac2

#confirm sample sheet matches the samples in the vcf
socal_sample_data<-read_delim("~/Dropbox/08_yhpa_072025/locator/final_runs/socal_run/sample_data_socal_final.txt")

colnames(socal.vcf.mac2@gt)
socal_sample_data$sampleID

socal_sample_data$sampleID %in% colnames(socal.vcf.mac2@gt)[-1]
colnames(socal.vcf.mac2@gt)[-1] %in% socal_sample_data$sampleID
```

In Bletchley run `final_socal_locator.sh`

```         
#!/bin/sh
#
#SBATCH --job-name=locator_yhpa             # Job Name
#SBATCH --partition=mlz-medium         # Name of the Slurm partition used
#SBATCH --nodelist=n028

locator --vcf /home/ramirezb/oratrix_locator/data/socal.mac2.unlinked.subsampled.vcf.gz --sample_data /home/ramirezb/oratrix_locator/data/sample_data_socal_final.txt --out /home/ramirezb/oratrix_locator/out_socal/oratrix --bootstrap --nboots 200 --seed 437
```

```{r}
#| output: false
setwd("~/Dropbox/08_yhpa_072025/locator/final_runs/socal_run/out_socal_final")
# Get list of all predloc files
socal_files <- list.files(pattern = "predlocs.*\\.txt")
socal_files
#remove full run
socal_files <- socal_files[-c(201)]

#This is the prediction from the full model trained on all SNPs (no resampling)
socal_full<-read_delim("oratrix_bootFULL_predlocs.txt")

# Read and bind them - all bootstrapped predictions
socal_all_preds <- socal_files %>%
  map_df(~ read_delim(.x, delim = ",", col_names = TRUE), .id = "file")

socal_individual_means <- socal_all_preds %>%
  group_by(sampleID) %>%
  summarize(mean_long = mean(x, na.rm = TRUE),
            mean_lat = mean(y, na.rm = TRUE))

socal_summary_stats<-socal_all_preds %>%
  group_by(sampleID) %>%
  summarize(mean_long = mean(x, na.rm = TRUE),
            mean_lat = mean(y, na.rm = TRUE),
            sd_x = sd(x, na.rm = TRUE),
            sd_y = sd(y, na.rm = TRUE))

#model performance
# R2(x)=0.6587273502642388
# R2(y)=0.7190529663421713
# mean validation error 3.632709017928652
# median validation error 3.264269199229253
```

```{r}
#showing 200 predictions
ggplot() +
  geom_sf(data = yhpa_map, fill = "gray95", color = "black") +
  geom_sf(data = mx_states, fill="gray95") +
  geom_sf(data = yhpa_shp, fill = "cornsilk2", show.legend = FALSE) +
  geom_point(data = socal_all_preds, aes(x =y, y =x, col = "all 200 bootstrapped predictions for unknown sample"), alpha = 0.4) +
  geom_point(data = socal_individual_means, aes(x = mean_lat, y = mean_long, color = "mean of 200 bootstraps"), size = 1) +
  geom_point(data = socal_full, aes(x = y, y = x,  color = "prediction from all samples - all SNPs with no resampling"), size = 1) +
  geom_point(data = socal_sample_data, aes(x = y, y = x, color = "all yhpa callibration points"), size = 1) +
  scale_color_manual(
    values = c(
      "all 200 bootstrapped predictions for unknown sample" = "palevioletred",
      "mean of 200 bootstraps" = "forestgreen",
      "prediction from all samples - all SNPs with no resampling" = "skyblue",
      "all yhpa callibration points" = "gray27"
    )
  ) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.margin = margin(t = 10, r = 10, b = 30, l = 10)) +
  labs(title = "Locator Southern California Predictions",
  x = "Longitude", y = "Latitude")
```

```{r}
#showing 95% boostrap ellipse
ggplot() +
  geom_sf(data = yhpa_map, fill = "gray95", color = "black") +
  geom_sf(data = mx_states, fill="gray95") +
  geom_sf(data = yhpa_shp, fill = "cornsilk2", show.legend = FALSE) +
  # geom_point(data = socal_all_preds, aes(x =y, y =x, col = "all 200 bootstrapped predictions for unknown sample"), alpha = 0.4) +
   # Ellipse around bootstrapped points
    stat_ellipse(data = socal_all_preds, aes(x = y, y = x, group = sampleID, color = "bootstrapped 95% ellipse"),
                 level = 0.95, linewidth = 0.4, linetype = 2, alpha = 0.5, 
                 inherit.aes = FALSE, show.legend = FALSE) +
  geom_point(data = socal_individual_means, aes(x = mean_lat, y = mean_long, color = "mean of 200 bootstraps"), size = 1) +
  geom_point(data = socal_full, aes(x = y, y = x,  color = "prediction from all samples - all SNPs with no resampling"), size = 1) +
  geom_point(data = socal_sample_data, aes(x = y, y = x, color = "all yhpa callibration points"), size = 1) +
      scale_color_manual(
    values = c(
      "bootstrapped 95% ellipse" = "palevioletred",
      "mean of 200 bootstraps" = "forestgreen",
      "prediction from all samples - all SNPs with no resampling" = "skyblue",
      "all yhpa callibration points" = "gray27"
    )
  ) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.margin = margin(t = 10, r = 10, b = 30, l = 10)) +
  labs(title = "Locator Southern California Predictions",
  x = "Longitude", y = "Latitude")
```

------------------------------------------------------------------------

#### Clean plots for manuscript

```{r}
#confiscated predictions
ggplot() +
  geom_sf(data = yhpa_map, fill = "gray95", color = "black") +
  geom_sf(data = mx_states, fill="gray95") +
  geom_sf(data = yhpa_shp, fill = "cornsilk2", show.legend = FALSE) +
  # geom_point(data = yhpa_all_preds, aes(x =y, y =x, col = "all 200 bootstrapped predictions for unknown sample"), alpha = 0.4) +
  # Ellipse around bootstrapped points
  stat_ellipse(data = yhpa_all_preds, aes(x = y, y = x, group = sampleID, color = "bootstrapped 95% ellipse"),
    level = 0.95, linewidth = 0.4, linetype = 2, alpha = 0.5, 
    inherit.aes = FALSE, show.legend = FALSE) +
  # geom_point(data = yhpa_individual_means, aes(x = mean_lat, y = mean_long, color = "mean of 200 bootstraps"), size = 1) +
  # geom_point(data = yhpa_full, aes(x = y, y = x,  color = "prediction from all samples - all SNPs with no resampling"), size = 1) +
  geom_point(data = yhpa_sample_data, aes(x = y, y = x, color = "all yhpa callibration points"), size = 1) +
      scale_color_manual(
    values = c(
      "bootstrapped 95% ellipse" = "palevioletred",
      "all yhpa callibration points" = "gray27"
    )
  ) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.margin = margin(t = 10, r = 10, b = 30, l = 10)) +
  labs(title = "Locator Confiscated YHPA Predictions",
  x = "Longitude", y = "Latitude")


#southern california predictions
ggplot() +
  geom_sf(data = yhpa_map, fill = "gray95", color = "black") +
  geom_sf(data = mx_states, fill="gray95") +
  geom_sf(data = yhpa_shp, fill = "cornsilk2", show.legend = FALSE) +
  # geom_point(data = socal_all_preds, aes(x =y, y =x, col = "all 200 bootstrapped predictions for unknown sample"), alpha = 0.4) +
   # Ellipse around bootstrapped points
    stat_ellipse(data = socal_all_preds, aes(x = y, y = x, group = sampleID, color = "bootstrapped 95% ellipse"),
                 level = 0.95, linewidth = 0.4, linetype = 2, alpha = 0.5, 
                 inherit.aes = FALSE, show.legend = FALSE) +
  # geom_point(data = socal_individual_means, aes(x = mean_lat, y = mean_long, color = "mean of 500 bootstraps"), size = 1) +
  # geom_point(data = socal_full, aes(x = y, y = x,  color = "prediction from all samples - all SNPs with no resampling"), size = 1) +
  geom_point(data = socal_sample_data, aes(x = y, y = x, color = "all yhpa callibration points"), size = 1) +
   scale_color_manual(
    values = c(
      "bootstrapped 95% ellipse" = "palevioletred",
      "all yhpa callibration points" = "gray27"
    )
  ) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.margin = margin(t = 10, r = 10, b = 30, l = 10)) +
  labs(title = "Locator Southern California Predictions",
  x = "Longitude", y = "Latitude")
```
