---
title: "YHPA.FST.pvalues.via.randomization"
format:
  html:
    code-fold: show
    code-tools: true
toc: true
toc-title: Document Contents
number-sections: true
embed-resources: true
---

### load R packages; read in vcf and sample sheet
```{r}
#| output: false
library(vcfR)
library(ggplot2)
library(SNPfiltR)
library(StAMPP)
library(adegenet)
v<-read.vcfR("~/Downloads/yhpa_final_filtered.vcf.gz")
samps<-read.csv("~/Downloads/Table1.for.manuscript.csv")
#make new column
samps[16,5]<-"SoCal"
samps[17,5]<-"SoCal"
samps[18,5]<-"SoCal"
samps$pop<-samps$Subspecies
```

### remove single auropalliata sample and then calculate FST between groups
```{r}
#remove sample
vsub<-v[,colnames(v@gt) != "ao_LSUMZ_39731"]
vsub
#remove invariant SNPs
vsub<-min_mac(vsub, 1)
vsub
#subset sampling file and fix pop IDs
samps<-samps[samps$sample_ID %in% colnames(vsub@gt),]
samps[16,5]<-"SoCal"
samps[17,5]<-"SoCal"
samps[18,5]<-"SoCal"

#reorder sample file to match vcf
samps<-samps[match(colnames(vsub@gt)[-1],samps$sample_ID),]

#convert vcfr to geno
gen<-vcfR2genlight(vsub)
#assign pops
pop(gen)<-samps$Subspecies
#calc FST
x<-stamppFst(gen)
#reassign
m<-x$Fsts
#fill in upper triangle of matrix
m[upper.tri(m)] <- t(m)[upper.tri(m)]
#melt for plotting
heat <- reshape::melt(m)
```

### plot pairwise FST
```{r}
#reorder factors for plotting
plot.order<-c("tresmariae","oratrix (west)","oratrix (east)","belizensis","SoCal","unknown")
heat$X1<-factor(heat$X1, levels=plot.order)
heat$X2<-factor(heat$X2, levels=plot.order)

#plot with labels
ggplot(data = heat, aes(x=X1, y=X2, fill=value)) + 
  geom_tile(color = "black", size=.5)+
  geom_text(data=heat,aes(label=round(value, 2)), size=2.25)+
  theme_minimal()+
  scale_fill_gradient2(low = "white", high = "darkgrey", space = "Lab", name="Fst") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, hjust = 1))

#ggsave(file="~/Desktop/YHPA.fst.pdf", units="in",width=4,height=3) #saves g

```


### use a loop to calculate the p-value associated with each pairwise Fst comparison based on 1K permutations
```{r, eval=FALSE}
#set up comparison dataframe
df<-data.frame(X1=c("oratrix (west)","oratrix (east)","belizensis","SoCal","unknown","oratrix (east)","belizensis","SoCal","unknown","belizensis","SoCal","unknown","SoCal","unknown","unknown"),
               X2=c("tresmariae","tresmariae","tresmariae","tresmariae","tresmariae","oratrix (west)","oratrix (west)","oratrix (west)","oratrix (west)","oratrix (east)","oratrix (east)","oratrix (east)","belizensis","belizensis","SoCal"),
               empirical.Fst=c(rep(NA, times=15)),
               pval=c(rep(NA, times=15)))

for (j in 12:nrow(df)){
  #isolate pops of interest
  vsub2<-vsub[,c(TRUE,samps$Subspecies == df[j,1] | samps$Subspecies == df[j,2])]
  colnames(vsub2@gt)
  vsub2
  
  #subset sampling file to only these samples
  samps.sub<-samps[samps$sample_ID %in% colnames(vsub2@gt),]
  
  #calculate empirical FST
  gen<-vcfR2genlight(vsub2)
  #assign pops
  pop(gen)<-samps.sub$Subspecies
  #calc FST
  x<-stamppFst(gen)
  #print empirical FST
  x$Fsts
  
  #loop to calculate FST with randomized sample assignment 1K times
  y<-c() #open empty vector to track results
  #loop that will randomize sample assignments while maintaining identical sample sizes, and store the resulting information
    for (i in 1:1000){
      #assign pops based on random number generator
      pop(gen)<-samps.sub$Subspecies[sample(1:nrow(samps.sub),size = nrow(samps.sub))]
      #Calc FST and store value
      y[i]<-stamppFst(gen)$Fsts[2,1]
      #inform that this iteration is complete
      #print(paste("iteration",i,"complete"))
    }

  #calc p-value
  table(y >= x$Fsts[2,1])
  mean(y >= x$Fsts[2,1])
  
  #make figure
  plot(density(y),main=paste("1K replicates of randomized sample assignments:\n",df[j,1],"vs.",df[j,2],", p =",round(mean(y >= x$Fsts[2,1]),4)),
       xlab = "Fst values")
  polygon(density(y), col = "slateblue1")
  abline(v=x$Fsts[2,1],lwd=2,lty=2,col="red")
  
  #store results in the dataframe
  df[j,3]<- x$Fsts[2,1] #store Fst
  df[j,4]<- mean(y >= x$Fsts[2,1]) #store pval

  #save the results to disk
  write.csv(y, file=paste0("~/Downloads/",df[j,1],"versus",df[j,2],".csv"), row.names = F)
}

#print the results
df
```

### re-run the analysis using stored data (above chunk only needs to be run once)
```{r}
#set up comparison dataframe
df<-data.frame(X1=c("oratrix (west)","oratrix (east)","belizensis","SoCal","unknown","oratrix (east)","belizensis","SoCal","unknown","belizensis","SoCal","unknown","SoCal","unknown","unknown"),
               X2=c("tresmariae","tresmariae","tresmariae","tresmariae","tresmariae","oratrix (west)","oratrix (west)","oratrix (west)","oratrix (west)","oratrix (east)","oratrix (east)","oratrix (east)","belizensis","belizensis","SoCal"),
               empirical.Fst=c(rep(NA, times=15)),
               pval=c(rep(NA, times=15)))

for (j in 1:nrow(df)){
  #isolate pops of interest
  vsub2<-vsub[,c(TRUE,samps$pop == df[j,1] | samps$pop == df[j,2])]
  colnames(vsub2@gt)
  vsub2
  
  #subset sampling file to only these samples
  samps.sub<-samps[samps$sample_ID %in% colnames(vsub2@gt),]
  
  #calculate empirical FST
  gen<-vcfR2genlight(vsub2)
  #assign pops
  pop(gen)<-samps.sub$pop
  #calc FST
  x<-stamppFst(gen)
  #print empirical FST
  x$Fsts

  #read in the precomputed dataframes
  y<-read.csv(paste0("~/Downloads/",df[j,1],"versus",df[j,2],".csv"))
  y$x<-round(y$x, 8)
  #make figure
  plot(density(y$x),main=paste("1K replicates of randomized sample assignments:\n",df[j,1],"vs.",df[j,2],", p =",round(mean(y$x >= round(x$Fsts[2,1],8)),4)),
       xlab = "Fst values")
  polygon(density(y$x), col = "slateblue1")
  abline(v=x$Fsts[2,1],lwd=2,lty=2,col="red")
  
  #store results in the dataframe
  df[j,3]<- x$Fsts[2,1] #store Fst
  df[j,4]<- round(mean(y$x >= round(x$Fsts[2,1],8)),4) #store pval
}
```

Because these FST values often just reflect sample size (e.g., comparisons with tresmariae are coming out with high p-values because small sample size in that population makes the probability of getting the accurate empirical sample assignments in the randomization procedure quite high - despite the fact that it is actually the most divergent population!) we chose not to include p-values in this manuscript.