---
title: "YHPA.subset.pairwise.FST"
format:
  html:
    code-fold: show
    code-tools: true
toc: true
toc-title: Document Contents
number-sections: true
embed-resources: true
---


### load R packages; read in vcf and sample sheet
```{r}
#| output: false
library(vcfR)
library(ggplot2)
library(SNPfiltR)
library(StAMPP)
library(adegenet)
v<-read.vcfR("~/Downloads/yhpa_final_filtered.vcf.gz")
samps<-read.csv("~/Downloads/Table1.for.manuscript.csv")
#make new column
samps$pop<-samps$Subspecies
#edit column to reflect north versus south split in eastern Mexico
samps$pop
samps$pop[c(42,21,14)]<-"oratrix (southeast)"
samps$pop[c(15:17)]<-"oratrix (northeast)"
samps$pop
```

### remove single auropalliata sample and then calculate FST between all groups
```{r}
#remove sample
vsub<-v[,colnames(v@gt) != "ao_LSUMZ_39731"]
vsub
#remove invariant SNPs
vsub<-min_mac(vsub, 1)
vsub
#subset sampling file and fix pop IDs
samps<-samps[samps$sample_ID %in% colnames(vsub@gt),]
samps[16,5]<-"SoCal"
samps[17,5]<-"SoCal"
samps[18,5]<-"SoCal"

#reorder sample file to match vcf
samps<-samps[match(colnames(vsub@gt)[-1],samps$sample_ID),]

#convert vcfr to geno
gen<-vcfR2genlight(vsub)
#assign pops
pop(gen)<-samps$Subspecies
#calc FST
x<-stamppFst(gen)
#reassign
m<-x$Fsts
#fill in upper triangle of matrix
m[upper.tri(m)] <- t(m)[upper.tri(m)]
#melt for plotting
heat <- reshape::melt(m)
```

### Now calculate FST with just populations of unknown ancestry plus eastern Mexico separated into north and south populations, plus do 1K random sample assignment replicates of each comparison to put a p-value on each pairwise FST
```{r, eval=FALSE}
#make new column
samps$pop<-samps$Subspecies
#edit column to reflect north versus south split in eastern Mexico
samps$pop
samps$pop[c(42,21,14)]<-"oratrix (southeast)"
samps$pop[c(15:17)]<-"oratrix (northeast)"
samps$pop

#set up comparison dataframe
df<-data.frame(X1=c("oratrix (northeast)","oratrix (southeast)","oratrix (northeast)","oratrix (southeast)"),
               X2=c("SoCal","SoCal","unknown","unknown"),
               empirical.Fst=c(rep(NA, times=4)),
               pval=c(rep(NA, times=4)))

for (j in 1:nrow(df)){
  #isolate pops of interest
  vsub2<-vsub[,c(TRUE,samps$pop == df[j,1] | samps$pop == df[j,2])]
  colnames(vsub2@gt)
  vsub2
  
  #subset sampling file to only these samples
  samps.sub<-samps[samps$sample_ID %in% colnames(vsub2@gt),]
  
  #calculate empirical FST
  gen<-vcfR2genlight(vsub2)
  #assign pops
  pop(gen)<-samps.sub$pop
  #calc FST
  x<-stamppFst(gen)
  #print empirical FST
  x$Fsts
  
  #loop to calculate FST with randomized sample assignment 1K times
  y<-c() #open empty vector to track results
  #loop that will randomize sample assignments while maintaining identical sample sizes, and store the resulting information
    for (i in 1:1000){
      #assign pops based on random number generator
      pop(gen)<-samps.sub$Subspecies[sample(1:nrow(samps.sub),size = nrow(samps.sub))]
      #Calc FST and store value
      y[i]<-stamppFst(gen)$Fsts[2,1]
      #inform that this iteration is complete
      print(paste("iteration",i,"complete"))
    }

  #calc p-value
  table(y >= x$Fsts[2,1])
  mean(y >= x$Fsts[2,1])
  
  #make figure
  plot(density(y),main=paste("1K replicates of randomized sample assignments:\n",df[j,1],"vs.",df[j,2],", p =",round(mean(y >= x$Fsts[2,1]),4)),
       xlab = "Fst values")
  polygon(density(y), col = "slateblue1")
  abline(v=x$Fsts[2,1],lwd=2,lty=2,col="red")
  
  #store results in the dataframe
  df[j,3]<- x$Fsts[2,1] #store Fst
  df[j,4]<- mean(y >= x$Fsts[2,1]) #store pval
  
  #save the results to disk
  write.csv(y, file=paste0("~/Downloads/",df[j,1],"-",df[j,2],".csv"), row.names = F)
}

#print the results
df
```

### visualize the results of the analysis from the chunk above using the stored data (chunk above only needs to be run once)
```{r}
#make new column
samps$pop<-samps$Subspecies
#edit column to reflect north versus south split in eastern Mexico
samps$pop
samps$pop[c(42,21,14)]<-"oratrix (southeast)"
samps$pop[c(15:17)]<-"oratrix (northeast)"
samps$pop

#set up dataframe
df<-data.frame(X1=c("oratrix (northeast)","oratrix (southeast)","oratrix (northeast)","oratrix (southeast)"),
               X2=c("SoCal","SoCal","unknown","unknown"),
               empirical.Fst=c(rep(NA, times=4)),
               pval=c(rep(NA, times=4)))

for (j in 1:nrow(df)){
  #isolate pops of interest
  vsub2<-vsub[,c(TRUE,samps$pop == df[j,1] | samps$pop == df[j,2])]
  colnames(vsub2@gt)
  vsub2
  
  #subset sampling file to only these samples
  samps.sub<-samps[samps$sample_ID %in% colnames(vsub2@gt),]
  
  #calculate empirical FST
  gen<-vcfR2genlight(vsub2)
  #assign pops
  pop(gen)<-samps.sub$pop
  #calc FST
  x<-stamppFst(gen)
  #print empirical FST
  x$Fsts

  #read in the precomputed dataframes
  y<-read.csv(paste0("~/Downloads/",df[j,1],"-",df[j,2],".csv"))
  y$x<-round(y$x, 8)
  #make figure
  plot(density(y$x),main=paste("1K replicates of randomized sample assignments:\n",df[j,1],"vs.",df[j,2],", p =",round(mean(y$x >= round(x$Fsts[2,1],8)),4)),
       xlab = "Fst values")
  polygon(density(y$x), col = "slateblue1")
  abline(v=x$Fsts[2,1],lwd=2,lty=2,col="red")
  
  #store results in the dataframe
  df[j,3]<- x$Fsts[2,1] #store Fst
  df[j,4]<- round(mean(y$x >= round(x$Fsts[2,1],8)),4) #store pval
}

#print results
df
```

We see that the p-values are not informative for these comparisons because of low sample size. Effectively, with only 3 individuals in each group, there are only 10 unique ways to shuffle the sample assignments. Therefore, ~10% of the time you get the empirically accurate sample assignments, giving you a p-value of 0.10, even though there is no sample assignment scheme that gives you a more extreme Fst value than the empirical one. It would essentially be like flipping a coin 3 times and then asking if there's statistical evidence that it's a weighted coin? Even if you got heads 3 times in a row, the probability of getting that result by random chance is 0.5 x 0.5 x 0.5 which is 0.125, or 12.5%. Essentially there is no outcome that is statistically significant at a threshold of p < 0.05. If you want to test the hypothesis you need greater sample size. For this reason, we chose not to include p-values in this analysis.


### Calc pairwise FST and fixed differences and make figure for manuscript
```{r}
library(vcfR)
library(ggplot2)
library(SNPfiltR)
library(StAMPP)
library(adegenet)
v<-read.vcfR("~/Downloads/yhpa_final_filtered.vcf.gz")
samps<-read.csv("~/Downloads/Table1.for.manuscript.csv")
#remove sample
vsub<-v[,colnames(v@gt) != "ao_LSUMZ_39731"]
vsub
#remove invariant SNPs
vsub<-min_mac(vsub, 1)
vsub
#subset sampling file and fix pop IDs
samps<-samps[samps$sample_ID %in% colnames(vsub@gt),]
samps[16,5]<-"SoCal"
samps[17,5]<-"SoCal"
samps[18,5]<-"SoCal"

#reorder sample file to match vcf
samps<-samps[match(colnames(vsub@gt)[-1],samps$sample_ID),]

#subset vcf and samps files
subsamps<-samps[c(13:17,21:42),]
subsamps$Subspecies[c(2,6,27)]<-"southeast"
subsamps$Subspecies[c(3,4,5)]<-"northeast"

subvcf<-v[,c(1,15:19,23:44)]
subvcf
colnames(subvcf@gt)
colnames(subvcf@gt)[-1] == subsamps$sample_ID

#convert vcfr to geno
gen<-vcfR2genlight(subvcf)
#assign pops
pop(gen)<-subsamps$Subspecies
#calc FST
x<-stamppFst(gen)
#reassign
m<-x$Fsts
#melt for plotting
heat <- reshape::melt(m)
#plot with labels
ggplot(data = heat, aes(x=X1, y=X2, fill=value)) + 
  geom_tile(colour = "black", linewidth = 0.5)+
  geom_text(data=heat,aes(label=round(value, 2)))+
  theme_minimal()+
  scale_fill_gradient2(low = "white", high = "red", space = "Lab", name="Fst") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, hjust = 1))

#identify the number of pairwise fixed differences between pops
mat<-extract.gt(subvcf)
conv.mat<-mat
conv.mat[conv.mat == "0/0"]<-0
conv.mat[conv.mat == "0/1"]<-1
conv.mat[conv.mat == "1/1"]<-2
conv.mat<-as.data.frame(conv.mat)
#convert to numeric
for (i in 1:ncol(conv.mat)){
  conv.mat[,i]<-as.numeric(as.character(conv.mat[,i]))
}

#show colnames to verify you're subsetting correctly
colnames(conv.mat) == subsamps$sample_ID

#make vector to fill with fixed diff values
f<-c()

#write for loop to calc number of fixed diffs between each pop
for (i in 1:nrow(heat)){
  #calc af of pop1 and pop2
  pop1.af<-(rowSums(conv.mat[,subsamps$Subspecies == heat$X1[i]], na.rm=T)/(rowSums(is.na(conv.mat[,subsamps$Subspecies == heat$X1[i]]) == FALSE)))/2
  pop2.af<-(rowSums(conv.mat[,subsamps$Subspecies == heat$X2[i]], na.rm=T)/(rowSums(is.na(conv.mat[,subsamps$Subspecies == heat$X2[i]]) == FALSE)))/2
  #store number of fixed differences
  f[i]<-sum(is.na(abs(pop1.af - pop2.af)) == FALSE & abs(pop1.af - pop2.af) == 1) #find fixed SNPs and add to vector
}

#add number of fixed diffs to df
heat$fixed<-f

#fix the assignments
heat$mixed<-heat$value
heat$mixed[c(c(5,9,10,13,14,15))]<-heat$fixed[c(5,9,10,13,14,15)]

#plot with labels
ggplot(data = heat, aes(x=X1, y=X2, fill=value)) + 
  geom_tile(colour = "black", linewidth = 0.5)+
  #scale_x_discrete(limits=levels(heat$X2)[c(1,7,2,3,4,5,6)], labels=levels(heat$X1))+ 
  #scale_y_discrete(limits=levels(heat$X2)[c(1,7,2,3,4,5,6)], labels=levels(heat$X1))+
  geom_text(data=heat,aes(label=round(mixed, 2)), size=2.5)+
  theme_minimal()+
  scale_fill_gradient2(low = "white", high = "red", space = "Lab", name="Fst") +
  theme(axis.text.x = element_text(angle = 45, vjust=.9, hjust = .9, size=12),
        axis.text.y = element_text(angle = 45, hjust = 1, size=12),
        axis.title.x = element_blank(), axis.title.y = element_blank())

```

